Formalizing Stack Safety as a Security Property

### 2021-09-29 submission4/main.tex
More appendicitis

To avoid cluttering the picture at the assembly level, we revert to assuming that the
argument {\tt a} is passed in a register, namely {\tt \%ra}.
The question is how the local variables {\tt x} and {\tt y} themselves
should be labelled in order for the property to correctly classify an integrity violation.
Our notion of domains is extended to include \(\passed{\depth,\depth'}\),
recording two depths for reasons explained below.
At the initial call, the address of {\tt x} is marked as passed, and {\tt f} is free to write to it. Then upon
return, {\tt main}'s frame is unsealed. At the second call it is the address of {\tt y} that is marked as passed,
and when {\tt f} instead tries to write to {\tt x}, it violates integrity.
%For that matter
%a future call with no arguments passed by reference would also violate integrity if it wrote
%to either variable.

@@

\paragraph*{Formalization of variable passing.}
We add extra information to our call
annotations to reflect that they may now pass variables on the stack, and that the locations
of those variables may be dynamic (as in the case of pass-by-reference).
A call annotation now includes a predicate relating machine states to the elements
that should be passed, expressed as offsets from the stack pointer.
\[\codemap \in \CODEMAPS ::= \WORDS \rightharpoonup \callmap(P)~\mbox{\rm where}~P \subseteq \WORDS\]
We extend the set of domains to include passed elements,
which are labeled with the range of depths of the caller that has passed them.
\[\begin{split}
\stackDom \in \STKDOMS ::= & \outside + \unsealed\\
& + \sealed{\depth} + \passed{\depth,\depth'}
\end{split}\]
The definition of context looks the same, but is based on the revised definition of \(\STKDOMS\):
\[\context \in \CONTEXTS ::= (\domMap \in \COMPONENTS \rightarrow \STKDOMS)
\times (\rts \in \listT (\target)) \]
The initial context again maps all elements to \(\unsealed\).
We straightforwardly describe how the sealing convention and passing predicate combine to
update a domain map at a call from depth \(\depth\).

>>>>

To avoid cluttering the picture at the assembly level, we revert to assuming that the
argument {\tt a} is passed in a register, namely {\tt \%ra}.
The question is how the local variables {\tt x} and {\tt y} themselves
should be labelled in order for the property to correctly classify an integrity violation.
Our notion of domains is extended to include \(\passed{\depth,\depth'}\),
recording two depths for reasons explained below.
At the initial call, the address of {\tt x} is marked as passed, and {\tt f} is free to write to it. Then upon
return, {\tt main}'s frame is unsealed. At the second call it is the address of {\tt y} that is marked as passed,
and when {\tt f} instead tries to write to {\tt x}, it violates integrity.

This extension to our model is formalized in Appendix \ref{app:argpass}.

@@

\paragraph*{Formalization of variable passing.}
\ref{app:argpass}

We add extra information to our call
annotations to reflect that they may now pass variables on the stack, and that the locations
of those variables may be dynamic (as in the case of pass-by-reference).
A call annotation now includes a predicate relating machine states to the elements
that should be passed, expressed as offsets from the stack pointer.
\[\codemap \in \CODEMAPS ::= \WORDS \rightharpoonup \callmap(P)~\mbox{\rm where}~P \subseteq \WORDS\]
We extend the set of domains to include passed elements,
which are labeled with the range of depths of the caller that has passed them.
\[\begin{split}
\stackDom \in \STKDOMS ::= & \outside + \unsealed\\
& + \sealed{\depth} + \passed{\depth,\depth'}
\end{split}\]
The definition of context looks the same, but is based on the revised definition of \(\STKDOMS\):
\[\context \in \CONTEXTS ::= (\domMap \in \COMPONENTS \rightarrow \STKDOMS)
\times (\rts \in \listT (\target)) \]
The initial context again maps all elements to \(\unsealed\).
We straightforwardly describe how the sealing convention and passing predicate combine to
update a domain map at a call from depth \(\depth\).
